---
title: "Challenge 8"
subtitle: "Diversity is the grandmother of invention"
output:
  html_document:
    df_print: paged
---
# Alpha Diversity Challenges
```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, include=TRUE)
```

## Background
The goal of this challenge is to give you experience with alpha diversity.

## Resources
The [Phyloseq Alpha diversity Tutorial](https://joey711.github.io/phyloseq/plot_richness-examples.html) will be helpful for this challenge.

## Data
For all of these challenges you will be using a lemur data phyloseq RDS that is available at `/data/tutorial_data/challenge6_lemur_full.rds`.

## Completing and Submitting
You must fill in the chunks below as indicated, but you are free to add other chunks too.  To submit this assignment for full credit you should *commit* and *push*:

1. This file (`challenge8_assignment.Rmd`)
2. The knited version of this file (`challenge8_assignment.html`)

These are the *ONLY* files you should include in your repo.  I strongly recommend that you put temporary files in a subdirectory of `/tmp`, for example `/tmp/scratch/challenge8`.  If you don't follow this advice, but instead put temporary files in your repo directory, you *must* be sure not to commit them to your repo. You will lose points if you commit any other files.


# Challenge Chunks
## Load Libraries
```{r}

```

## Define Paths
```{r}

```

## Check Phyloseq RDS
Load your phyloseq RDS and `print` it just to be sure things look sane
```{r}

```

## Basic Alpha Diversity Plot
Make alpha diversity plots using two different measures of alpha diversity.  Choose one measure based on rare taxa (i.e. "weirdos") and choose a second measure based on surprise (i.e. "gambling").  Group samples by any categorical variable you like.  

```{r}

```

## Alpha Diversity Boxplot
Do you see any groups that show particularly high or low alpha diversity? A boxplot is a nice way to summarize and compare 1D scatterplots.  Try adding boxplots to your alpha diversity plots.

```{r}

```

## Bonus: Alpha Diversity
Calculate *four* different measures of alpha diversity for each sample in the dataset and put the results in a dataframe with samples as rows and alpha diversity measures as columns

> Hint there is a phyloseq function that makes this *very* easy

```{r}

```

# sessionInfo
It is always a good idea to capture the sessionInfo information so you know what versions of R and libraries you used!
```{r echo=TRUE, include=TRUE}
sessionInfo()
```


